---
title: "workout1"
author: "Richard Min"
date: "10/2/2018"
output: github_document
---

```{r}
library(readr)
library(ggplot2)
```

```{r horizontal barchart1}
ggplot(teams, aes(x = reorder(teams$team, teams$salary), y = teams$salary)) +
  geom_bar(stat='identity') +
  coord_flip() + xlab("Teams") + ylab("Salary (in millions") + ggtitle("NBA Teams Ranked by Total Salary")
```

```{r horizontal barchart 2}
avg_points = mean(teams$points)

ggplot(teams, aes(x = reorder(teams$team, teams$points), y = teams$points)) + geom_bar(stat='identity') + coord_flip() + xlab('Teams') + ylab('Total Points') + ggtitle('NBA Teams Ranked by Total Points') + geom_hline(aes(yintercept = avg_points, color = 'red'))

```

```{r horizontal barchart 3}
avg_efficiency = mean(teams$efficiency)
ggplot(teams, aes(x = reorder(teams$team, teams$efficiency), y = teams$efficiency)) + geom_bar(stat='identity') + coord_flip() + xlab("Teams") + ylab("Efficiency") + ggtitle("NBA Teams Ranked by Total Efficiency") + geom_hline(aes(yintercept = avg_efficiency, color = 'red'))

```

```{r horizontal barchart4}


```

###_Comments and Reflections_  
1. Yes this was the first time I have ever worked on this kind of project. It was pretty difficult.  
2. Yes, this was my first time using relative paths. It is important to be able to access the files inside depending if they are in a different directory.   
3. Yes, this was my first time using R script. I thought it was fine.  
4. Using relative path was hard because it was my first time dealing with it. It was a bit tricky to get used to it. I have to remember where my working depository at all times.  
5. Nothing was easy despite not seeing it in class.  
6. Yes, I had previous students help me with understanding relative path. Uploading to GitHub was also tricky.  
7. It took me about 15 hours to finish.  
8. Uploading to GitHub and understanding relative path took the most time.  
9. I thought that relative paths was interesting.  
